Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-09-10 journal-draft/ettdoc.tex
change ccc to cc

We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel is available equals to the rate of false negative.
The secondary users make clustering decisions based on the imperfect spectrum sensing.
After the clustering process is completed, we correct the spectrum availability with the ground truth.
Then certain formed clusters may be affected as their CCCs which are obtained due to false negative will be revoked.
%When the clustering process is completed, we will examine the performances on robustness and cluster size control with the group truth spectrum availability.
%C3
\end{itemize}

@@

Figure~\ref{false_negative_ccc} shows the average number of CCCs decrease slightly when the false negative rate increases.
The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}
%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.

@@

\subsection{Insights Obtained from the Simulation}
The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
First, different from the assumption adopted in all the previous works, the average number of CCCs per cluster can tell the robustness against the increasing influence of the primary users.
Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
Third, as distributed schemes, the variants of ROSS outperform SOC considerably in four aspects.
\begin{itemize}
\item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
\item The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
\item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
\item The variants of ROSS are more resilient against the imperfect spectrum sensing.
\end{itemize}

>>>>

We assume when a secondary user is within the transmission range of an active primary user, the probability that it misdetects and thus regards a channel is available equals to the rate of false negative.
The secondary users make clustering decisions based on the imperfect spectrum sensing.
After the clustering process is completed, we correct the spectrum availability with the ground truth.
Then certain formed clusters may be affected as their CCs which are obtained due to false negative will be revoked.
%When the clustering process is completed, we will examine the performances on robustness and cluster size control with the group truth spectrum availability.
%C3
\end{itemize}

@@

Figure~\ref{false_negative_ccc} shows the average number of CCs decrease slightly when the false negative rate increases.
The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}
%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.

@@

\subsection{Insights Obtained from the Simulation}
The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
First, different from the assumption adopted in all the previous works, the average number of CCs per cluster can tell the robustness against the increasing influence of the primary users.
Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
Third, as distributed schemes, the variants of ROSS outperform SOC considerably in four aspects.
\begin{itemize}
\item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
\item The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
\item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
\item The variants of ROSS are more resilient against the imperfect spectrum sensing.
\end{itemize}
